Verifying Demonstrations

### 2018-11-16 paper/protocol.tex
changing the strength function
edits first part of protocol section

We now present \CROCUS, a protocol for securely and privately verifying crowd counts.
The protocol consists of five phases: setup, join, participation, submission and verification phases.
The setup is described in \cref{ProtocolSetup}.
The join, participation and submission phases are detailed in \cref{ProtocolDuring}.
Finally, the verification phase is presented in \cref{ProtocolVerification}.

@@

In the case \emph{without} trusted witnesses, the verifier simply define 
\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\) and set \(\theta\) to the 
desired threshold.

>>>>

We now present \CROCUS, a protocol for privately verifyiable crowd counts.
The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
join, participation, submission (all in in \cref{ProtocolDuring} ) and
verification (in \cref{ProtocolVerification}).

@@

In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
